---
title: "ADFG_FRP_2018"
author: "Wendel Raymond"
date: "January 9, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Alaska Department of Fish and Game Fisheries Resource permit reporting
This script will take raw "tall" data, from multiple parent sources if necessary, and format it for the FRP reporting form.
```{r libraries}
library(dplyr)
library(tidyr)
```

## Data
```{r data}
# Eelgrass Site
eg.clam <- read.csv("E:/wraymond2/My Documents/Graduate School/APECS_master/ALL_DATA/Clam_transect_2018_RAW.csv", stringsAsFactors = FALSE, header = TRUE)

# Eelgrass Biometrics (lab data)
eg.bio <- read.csv("E:/wraymond2/My Documents/Graduate School/APECS_master/ALL_DATA/eelgrass_biometrics_2018_RAW.csv", stringsAsFactors = FALSE, header = TRUE)

# Eelgrass Transect
eg.tran <- read.csv("E:/wraymond2/My Documents/Graduate School/APECS_master/ALL_DATA/Eelgrass_transect_2018_RAW.csv", stringsAsFactors = FALSE, header = TRUE)

# Crab Pot
crab.dat <- read.csv("E:/wraymond2/My Documents/Graduate School/APECS_master/All_DATA/Crab_pots_2018_RAW.csv", header = TRUE, stringsAsFactors = FALSE)

# Beach Seine
fish.dat <- read.csv("E:/wraymond2/My Documents/Graduate School/APECS_master/ALL_DATA/Beach_seine_eelgrass_2018_RAW.csv", stringsAsFactors = FALSE, header = TRUE)

fish.dat$unmeasured <- as.numeric(fish.dat$unmeasured)

# Biomarkers
biom.dat <- read.csv("E:/wraymond2/My Documents/Graduate School/APECS_master/ALL_DATA/Biomarker_collections_2018_RAW.csv", stringsAsFactors = FALSE, header = TRUE)
```

## Eelgrass
We did not directly count eelgrass that we collected but our protocol was to collect all shoots in a 15cm diamerter ring in 8 quadrats at all 6 of our sites. To that end the number of shoots collected wil be the calculated shoot density per meter square * 0.17671, the area of the ring.
```{r n eelgrass}
eg.tran$eelgrass_shoots_meter <- eg.tran$eelgrass_shoots_0.25msq * 4
eg.tran$shoots_collected <- round(eg.tran$eelgrass_shoots_meter * 0.17671, 0)

eg <- eg.tran %>% 
  group_by(site) %>% 
  summarize(Site = unique(place_name),
            Date = unique(date),
            Latitude = unique(latitude),
            Longitude = unique(longitude),
            Eelgrass_shoots = sum(shoots_collected))

eg <- data.frame(eg[,1:5], "sp" = "Eelgrass", "collection_method" = "hand", eg[,6])
colnames(eg)[8] <- "count"
```

## Grazers - small inverts
This will come from the biometrics data
```{r n grazers}
## Summarise ##
graz <- data.frame(
  eg.bio %>% 
    group_by(site) %>% 
    summarise(Idotea_rascata = sum(idotea_count, na.rm = TRUE),
              Gammarid_amphipod = sum(amphipod_count, na.rm = TRUE),
              Caprella_alaskana = sum(caprellid_count, na.rm = TRUE),
              Lottia_sp = sum(limpet_count, na.rm = TRUE),
              Littorina_sp = sum(gastropod_count, na.rm = TRUE))
)

## Convert to tall ##
graz <- gather(graz, sp, count, Idotea_rascata:Littorina_sp)

## Add colelction method ##
graz <- data.frame(graz[,1:2], "collection_method" = "hand", graz[,3])
colnames(graz)[4] <- "count"
```

## Crabs
This data will come from the crab pot data. We also caught fish in pots so that will be extracted here and added to fish data later.
```{r n crabs}
## Crabs from pots ##
crab <- data.frame(
  crab.dat %>% 
    filter(taxon == "Decapoda") %>% 
    group_by(site, species_scientific) %>% 
    summarise(n = n())
)

## Fish from pots ##
fish.crab <- data.frame(
  crab.dat %>% 
    filter(taxon == "Vertebrata") %>% 
    group_by(site, species_scientific) %>% 
    summarise(n = n())
)
```

## Fish
This data will come from the beach seine data. We also caught crabs in the beach seine so that will be extracted here and added to the crab derived above.
```{r n fish}
fish.m <- fish.dat %>%
  filter(taxon == "Vertebrata") %>%
  filter(fork_length > 0)

fish.um <- fish.dat  %>%
  filter(taxon == "Vertebrata") %>% 
  filter(unmeasured != "estimate") %>% # assume that infield estimates are accurate
  filter(unmeasured > 0)

fish.sum <- fish.m %>%
  group_by(site, species_scientific) %>% 
  summarise(measured = n())

fish.sum.um <- fish.um %>%
  group_by(site, species_scientific) %>% 
  summarise(um = sum(unmeasured))

fish.sum <- merge(fish.sum, fish.sum.um, by = c("site", "species_scientific"), all = TRUE)
fish.sum$um[is.na(fish.sum$um)] <- 0
fish.sum $total <- fish.sum$measured + fish.sum$um

## Fish from seine ##
fish <- data.frame(
  fish.sum %>%
    group_by(site, species_scientific) %>% 
    summarise(n = sum(total))
)

## Crabs from seine ##
crab.fish <- data.frame(
  fish.dat %>%
    filter(taxon != "Vertebrata") %>% 
    group_by(site, species_scientific) %>% 
    summarise(n = sum(unmeasured))
)
```

## Clams
These data will come from the clam transect data.
```{r n clams}
## Crabs from pots ##
clam <- data.frame(
  eg.clam %>% 
    group_by(site, species_scientific) %>% 
    summarise(n = n())
)

colnames(clam)[2] <- "sp"
clam <- cbind(clam[,1:2], "collection_method" = "hand", clam[,3])
colnames(clam)[4] <- "count"
```

## Biomarker Collections
These data will come from the biomarker colelctions. It is imporant to note that there is overlap in theses collections and collections made in other activities. The only species that are unique collections from this data are.

1. Idotea
2. Limpet
3. Helmet crab
4. kelp crab
5. Dock shrimp
6. Red rock crab
7. Dungeness crab
8. Nereid worm
9. Spaghetti worm
10. Ulva
11. Sugar kelp

Also note that some samples pooled multiple individuals so the n collected is really n_pooled
```{r n biomarker}
# biomarker collections that are not dubplicated
biom <- data.frame(
  biom.dat %>% 
    filter(Species_common == "Idotea" | Species_common == "Limpet" | Species_common == "Helmet crab" | Species_common == "Kelp crab" | Species_common == "Dock shrimp" | Species_common == "Red rock crab" | Species_common == "Dungeness crab" | Species_common == "Nereid worm" | Species_common == "Spaghetti worm" | Species_common == "Ulva" | Species_common == "Sugar kelp") %>% 
    group_by(Site, Species_scientific) %>% 
    summarise(n = sum(n_pooled))
) 

# fix nas
biom$n[is.na(biom$n)] <- 6

# clean up
colnames(biom)[2] <- "sp"
biom <- cbind(biom[,1:2], "collection_method" = "hand", biom[,3])
colnames(biom)[4] <- "count"
colnames(biom)[1] <- "site"

# Add site data #
biom <- merge(biom, eg[,1:5], by = "site")
colnames(biom)[5] <- "place_name"
```


## Bring it all together now
Get all the summaries above into one nice happy table! Including site identifier information.
```{r}
## All the crabs ##
crab <- merge(crab, crab.fish, by = c("site", "species_scientific"), all = TRUE)
crab[is.na(crab)] <- 0
crab$count <- (crab$n.x + crab$n.y)
crab[crab == ""] <- "Decapoda"
colnames(crab)[2] <- "sp"
crab <- cbind(crab[,1:2], "collection_method" = "crab pot", crab[,5])
colnames(crab)[4] <- "count"

## All the fish ##
fish <- merge(fish, fish.crab, by = c("site", "species_scientific"), all = TRUE)
fish[is.na(fish)] <- 0
fish$count <- (fish$n.x + fish$n.y)
colnames(fish)[2] <- "sp"
fish <- cbind(fish[,1:2], "collection_method" = "beach seine", fish[,5])
colnames(fish)[4] <- "count"

## Final Combine ##
dat <- eg[,1:5]

# standard data #
counts <- rbind.data.frame(crab, fish, eg[,c(1,6:8)], graz, clam)

# add biomarker
counts <- merge(counts, biom[,1:4], by = c("site", "sp", "collection_method"), all = TRUE)

# clean up 
counts$count.x[is.na(counts$count.x)] <- 0
counts$count.y[is.na(counts$count.y)] <- 0

counts$count <- counts$count.x + counts$count.y

counts <- counts[,c(1:3, 6)]

# Merge #
dat <- merge(dat, counts, by = "site", all = TRUE)

# add life stage #
dat <- cbind(dat[,1:7], data.frame(Life_stage = "adult/non-larval juveniles"), dat[,8])
colnames(dat)[9] <- "Count"

# remove site
dat <- dat[,2:9]

## Just group by species ##
sp <- dat %>% 
  group_by(sp) %>% 
  summarise(total = sum(Count))

## Just fish for IACUC ##
fish.sp <- fish %>% 
  group_by(sp) %>% 
  summarise(total = sum(count))

fish.sp$total_retained <- 0
```

## Export
```{r}
write.csv(dat, "ADFG_collections_CF_18_056.csv", row.names = FALSE)

write.csv(fish.sp, "../../IACUC/IACUC_collections_2018.csv", row.names = FALSE)
```