---
title: "ADFG_FRP_FISH414_2019"
author: "Wendel Raymond"
date: "December 3, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Alaska Department of Fish and Game Fisheries Resource permit reporting
This script will take raw "tall" data, from multiple parent sources if necessary, and format it for the FRP reporting form.
```{r libraries}
library(dplyr)
library(tidyr)
```

## Data
```{r data}
# Beach Seine
fish.dat <- read.csv("C:/Users/Wendubs/Documents/Graduate School/Teaching/FISH 414/Beach_Seine_Data_2019.csv", stringsAsFactors = FALSE, header = TRUE)

fish.dat$unmeasured <- as.numeric(fish.dat$unmeasured)
```

## Fish
This data will come from the beach seine data. We also caught crabs in the beach seine so that will be extracted here and added to the crab derived above.
```{r n fish}
fish.m <- fish.dat %>%
  filter(fork.length..mm. > 0)

fish.um <- fish.dat  %>%
  filter(unmeasured > 0)

fish <- fish.m %>%
  group_by(Site, scientific.name) %>% 
  summarise(measured = n(),
            mean_size = mean(fork.length..mm., na.rm = TRUE))

```

## Final clean up 
```{r}
fish[is.na(fish)] <- 0

fish <- merge(fish, unique(fish.dat[, c(1,2,15,16)]), by = "Site", all.x = TRUE)

fish$Disposition <- "released live into wild"
fish$Life_Stage <- "adult/non-larval juveniles"

fish <- cbind(fish[, c(5,1,6,7,2, 4, 9,3,8)])
```

## Export
```{r}
write.csv(fish, "ADFG_collections_CF_19_048.csv", row.names = FALSE)
```