---
title: "ADFG_FRP_2017"
author: "Wendel Raymond"
date: "January 26, 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Alaska Department of Fish and Game Fisheries Resource permit reporting
This script will take raw "tall" data, from multiple parent sources if necessary, and format it for the FRP reporting form.
```{r libraries}
library(dplyr)
library(tidyr)
```


## Data
```{r data}
# Eelgrass Site
eg.site <- read.csv("E:/wraymond2/My Documents/Graduate School/APECS-master/ALL_DATA/seagrass_site_2017_RAW.csv", stringsAsFactors = FALSE, header = TRUE)

# Eelgrass Biometrics (lab data)
eg.bio <- read.csv("E:/wraymond2/My Documents/Graduate School/APECS-master/ALL_DATA/seagrass_biometrics_CLEAN.csv", stringsAsFactors = FALSE, header = TRUE)

# Eelgrass Transect
eg.tran <- read.csv("E:/wraymond2/My Documents/Graduate School/APECS-master/ALL_DATA/seagrass_transect_2017_RAW.csv", stringsAsFactors = FALSE, header = TRUE)

# Crab Pot
crab.dat <- read.csv("E:/wraymond2/My Documents/Graduate School/APECS-master/All_DATA/seagrass_crab_pot_2017_RAW.csv", header = TRUE, stringsAsFactors = FALSE)

# Beach Seine
fish.dat <- read.csv("E:/wraymond2/My Documents/Graduate School/APECS-master/ALL_DATA/seagrass_beach_seine_data_2017_RAW.csv", stringsAsFactors = FALSE, header = TRUE)

fish.dat$unmeasured <- as.numeric(fish.dat$unmeasured)
```

## Eelgrass
We did not directly count eelgrass that we collected but our protocol was to collect 5 shoots in 8 quadrats at all 21 of our sites = 840 individiuals. But we incedentidally collected ~ 10 more shoots at each site, so a total of 1050 for 50 per site.
```{r n eelgrass}
eg <- data.frame("site" = unique(eg.site$site), "sp" = rep("Zostera_marina", 21), "collection_method" = "hand", "count" = 50)
```

## Grazers - small inverts
This will come from the biometrics data
```{r n grazers}
## Summarise ##
graz <- data.frame(
  eg.bio %>% 
    group_by(site) %>% 
    summarise(Idothea_rascata = sum(iso_count, na.rm = TRUE),
              Gammarid_amphipod = sum(gamm_amph_count, na.rm = TRUE),
              Caprella_alaskana = sum(caprel_count, na.rm = TRUE),
              Lottia_sp = sum(limpet_count, na.rm = TRUE),
              Littorina_sp = sum(gastropod_count, na.rm = TRUE),
              Polychaeta_sp = sum(polychaete_count, na.rm = TRUE))
)

## Convert to tall ##
graz <- gather(graz, sp, count, Idothea_rascata:Polychaeta_sp)

## Add colelction method ##
graz <- data.frame(graz[,1:2], "collection_method" = "hand", graz[,3])
colnames(graz)[4] <- "count"
```

## Crabs
This data will come from the crab pot data. We also caught fish in pots so that will be extracted here and added to fish data later.
```{r n crabs}
## Crabs from pots ##
crab <- data.frame(
  crab.dat %>% 
    filter(taxon == "Decapoda") %>% 
    group_by(site, species_scientific) %>% 
    summarise(n = n())
)

## Fish from pots ##
fish.crab <- data.frame(
  crab.dat %>% 
    filter(taxon == "Vertebrata") %>% 
    group_by(site, species_scientific) %>% 
    summarise(n = n())
)
```

## Fish
This data will come from the beach seine data. We also caught crabs in the beach seine so that will be extracted here and added to the crab derived above.
```{r n fish}
fish.m <- fish.dat %>%
  filter(taxon == "Vertebrata") %>%
  filter(fork_length > 0)

fish.um <- fish.dat  %>%
  filter(taxon == "Vertebrata") %>% 
  filter(unmeasured != "estimate") %>% # assume that infield estimates are accurate
  filter(unmeasured > 0)

fish.sum <- fish.m %>%
  group_by(site, species_scientific) %>% 
  summarise(measured = n())

fish.sum.um <- fish.um %>%
  group_by(site, species_scientific) %>% 
  summarise(um = sum(unmeasured))

fish.sum <- merge(fish.sum, fish.sum.um, by = c("site", "species_scientific"), all = TRUE)
fish.sum$um[is.na(fish.sum$um)] <- 0
fish.sum $total <- fish.sum$measured + fish.sum$um

## Fish from seine ##
fish <- data.frame(
  fish.sum %>%
    group_by(site, species_scientific) %>% 
    summarise(n = sum(total))
)

## Crabs from seine ##
crab.fish <- data.frame(
  fish.dat %>%
    filter(taxon != "Vertebrata") %>% 
    group_by(site, species_scientific) %>% 
    summarise(n = sum(unmeasured))
)
```

## Bring it all together now
Get all the summaries above into one nice happy table! Including site identifier information.
```{r}
## All the crabs ##
crab <- merge(crab, crab.fish, by = c("site", "species_scientific"), all = TRUE)
crab[is.na(crab)] <- 0
crab$count <- (crab$n.x + crab$n.y)
crab[crab == ""] <- "Decapoda"
colnames(crab)[2] <- "sp"
crab <- cbind(crab[,1:2], "collection_method" = "crab pot", crab[,5])
colnames(crab)[4] <- "count"

## All the fish ##
fish <- merge(fish, fish.crab, by = c("site", "species_scientific"), all = TRUE)
fish[is.na(fish)] <- 0
fish$count <- (fish$n.x + fish$n.y)
colnames(fish)[2] <- "sp"
fish <- cbind(fish[,1:2], "collection_method" = "beach seine", fish[,5])
colnames(fish)[4] <- "count"

## Final Combine ##
dat <- eg.site[,1:5]

counts <- rbind.data.frame(crab, fish, eg, graz)

dat <- merge(dat, counts, by = "site", all = TRUE)

dat <- cbind(dat[,1:7], data.frame(Life_stage = "adult/non-larval juveniles"), dat[,8])
colnames(dat)[9] <- "Count"

## Just group by species ##
sp <- dat %>% 
  group_by(sp) %>% 
  summarise(total = sum(Count))

## Just fish for IACUC ##
fish.sp <- fish %>% 
  group_by(sp) %>% 
  summarise(total = sum(count))

fish.sp$total_retained <- 0
```

## Export
```{r}
write.csv(dat, "ADFG_collections_CF_17_050.csv", row.names = FALSE)

write.csv(fish.sp, "../../IACUC/IACUC_collections_2017.csv", row.names = FALSE)
```

